---
title: "TidyTuesday Week 39"
author: "Dominik Ziaja"
date: "2022-10-01"
output:
  html_document:
    toc: true
    number_section: true
    toc_float: true
    code_folding: hide
    theme: cerulean
---
# Loading necessities
```{r}
library(tidyverse)
library(showtext)
library(fontawesome)
library(stringr)
library(geojsonio)
library(rgeos)
library(broom)
library(ggthemes)
```


# Setting up fonts that are used
```{r}
font_add_google("Montserrat")
font_headlines <- "Montserrat"
font_add_google("Cousine")
font_text <- "Cousine"
# get the path of font awesome
fa_brands_path <- systemfonts::font_info(family = "Font Awesome 6 Brands")[["path"]]
# add the font under the name of "fa-brands"
font_add(family = "fa-brands", fa_brands_path)

showtext_auto()
```

# Define used colors
```{r}
colors.factors <- c("#E69F00",
                    "#56B4E9",
                    "#F0E442",
                    "#009E73",
                    "#0072B2",
                    "#D55E00",
                    "#CC79A7",
                    "#000000",
                    "#7C7C7C")

colors.factors.second <- c("#BBCC33",
                           "#AAAA00",
                           "#77AADD",
                           "#EE8866",
                           "#EEDD88",
                           "#FFAABB",
                           "#99DDFF",
                           "#44BB99",
                           "#DDDDDD")

background.color <- ""

```

# Load data
```{r}
data.artists <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-09-27/artists.csv')
US.hexbin <- geojson_read("us_states_hexgrid.geojson", what = "sp")
```

# Data wrangling
```{r}

# Since I want to do two plots, first the tidying that's important for both
# plots
data.artists.tidied <- data.artists %>%
  mutate(artists_share = case_when(artists_n == 0 ~ 0,
                                   TRUE ~ artists_share),
         type = tolower(type)) %>%
  mutate(type_summarised = case_when(
            grepl("music", type, fixed=T) ~ "music",
            grepl("architects", type, fixed=T) ~ "architecture",
            type == "entertainers" | type == "announcers" ~ "public",
            type == "producers and directors" | 
              type == "actors" |
              type == "Dancers and Choreographers" ~ "cinema/shows",
            type == "Writers and Authros" | type == "Photographers" ~ "media",
            TRUE ~ type)) %>%
  filter(!is.na(artists_share))

# Data for the stacked barplot showing number of total workers and artists
data.barplot <- data.artists.tidied %>%
  mutate(total_workers_excl_artists = all_workers_n - artists_n) %>%
  group_by(state) %>%
  summarise(across(c("artists_n", "total_workers_excl_artists"), sum)) %>%
  pivot_longer(artists_n:total_workers_excl_artists,
               names_to = "Occupation",
               values_to = "Count") %>%
  mutate(Occupation = 
           case_when(Occupation == "artists_n" ~ "artist",
                    Occupation == "total_workers_excl_artists" ~ "non-artist")) %>%
  arrange(desc(Count))

# Reformat hexbin map to allow merging
US.hexbin@data <- US.hexbin@data %>%
  mutate(google_name = gsub(" \\(United States\\)", "", google_name))

# make hexbin ggplotable
US.hexbin.fortified <- tidy(US.hexbin, region = "google_name")

# calculate centers of each polygon
centers <- cbind.data.frame(data.frame(gCentroid(US.hexbin, byid=T), id=US.hexbin@data$iso3166_2))

# Data for the US hexagon bin plot
data.hexa <- data.artists.tidied %>%
  filter(state != "Puerto Rico") %>%
  group_by(state, race, type_summarised) %>%
  summarise(artists_share_summed = sum(artists_share)) %>%
  group_by(state, race) %>%
  # keeps the group combination with the maximum value
  top_n(1, artists_share_summed) %>%
  group_by(state) %>%
  distinct(race, .keep_all=T) %>%
  mutate(
    type_summarised = case_when(
      artists_share_summed == 0 ~ "No artist shares",
      TRUE ~ type_summarised),
    type_summarised = factor(type_summarised,
                                  levels = c("architecture",
                                             "cinema/shows",
                                             "dancers and choreographers",
                                             "designers",
                                             "fine artists, art directors, and animators",
                                             "music",
                                             "photographers",
                                             "public",
                                             "writers and authors",
                                             "No artist shares")),
    race = factor(race, levels = c("Asian",
                                   "African-American",
                                   "Hispanic",
                                   "White",
                                   "Other"))) %>%
  left_join(US.hexbin.fortified, by = c("state" = "id"))
  
  
```

# Plot the barplot
```{r}
plot.bar.artistproportion <- ggplot(data = data.barplot,
                                    aes(x = reorder(state, Count),
                                        y = Count, fill = Occupation),
                                    color = "white") +
  geom_bar(stat = "identity") +
  coord_flip()

plot(plot.bar.artistproportion)

ggsave("barplot.png", width = 18, height = 10)
```

# Plot the hexagon data
```{r fig.width = 20 fig.height=10}
plot.hexa.artistsshare <- ggplot(data = data.hexa) +
  geom_polygon(aes(x = long, y = lat, group = group, fill = type_summarised),
               color = "white") +
  facet_wrap(~race, scale = "free") +
  geom_text(data = centers, aes(x = x, y = y, label = id),
            size = 5) +
  scale_fill_manual("Artists in the field of",
                    values = colors.factors.second,
                    labels = c("Architecture",
                               "Cinema and shows",
                               "Dancing",
                               "Design",
                               "Fine art and Art direction",
                               "Music",
                               "Photography",
                               "Writing",
                               "No artists employed")) +
  theme_classic(base_size = 18) +
  theme(
    panel.grid = element_blank(),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(color = "black", size = 20),
    panel.border = element_blank(),
    axis.ticks = element_blank(),
    legend.position = "top",
    legend.key.size = unit(.5, "cm")) +
  guides(fill = guide_legend(ncol = 5))

plot(plot.hexa.artistsshare)

ggsave("hexamap.png", width = 8, height = 5)
```

```{r}
library(cowplot)

aligned <- plot_grid(plot.bar.artistproportion, plot.hexa.artistsshare)
ggdraw(plot.hexa.artistsshare) + 
  draw_plot(plot.bar.artistproportion, x = 0.75, y = 0.01, height = 0.4, width = 0.3)

ggsave("test.png", width = 10, height = 6)
```


## List of professions and how to summarise these:
* ~~architects~~ $\rightarrow$ architecture
* ~~Landscape architects~~ $\rightarrow$ architecture
* Fine Artists, Art directors and animators
* Designers
* ~~Actors~~ $\rightarrow$ cinema/shows
* ~~Producers and Directors~~ $\rightarrow$ cinema/shows
* ~~Dancers and Choreographers~~ $\rightarrow$ cinema/shows
* ~~Musicians~~ $\rightarrow$ music
* ~~Music Directors and Composers~~ $\rightarrow$ music
* ~~Entertainers~~ $\rightarrow$ public
* ~~Announcers~~ $\rightarrow$ public
* ~~Writers and Authors~~ $\rightarrow$ media
* ~~Photographers~~ $\rightarrow$ media